R dyntrace report

### 2018-04-03 graphs/report-basic-info.Rmd
Errors. Also, the file is not here.

``` {r, "basic info", include=FALSE}
aggregated_functions <- load_local_csv("aggregated_functions.csv") #

@@

basic_info <- 
  load_local_csv("basic_info.csv") %>%
  group_by(name) %>%
  summarise(
    datasets=paste(name, collapse=", "),
    n.datasets=n(),
    n.functions=sum(n.functions),
    n.calls=sum(n.calls),
    n.promises=sum(n.promises),
    n.promise.forces=sum(n.promise.forces),
    n.promise.lookups=sum(n.promise.lookups), 
    n.alien.promises=sum(n.alien.promises),
    n.alien.promise.forces=sum(n.alien.promise.forces)
  )

@@

 aggregate_basic_info <- 
   basic_info %>% summarise(
     name="*",
     datasets=paste(name, collapse=", "),
     n.datasets=n(),
     n.functions=NA # FIXME (aggregated_functions %>% count %>% pull(n)),
     n.calls=sum(n.calls),
     n.promises=sum(n.promises),
     n.promise.forces=sum(n.promise.forces),
     n.promise.lookups=sum(n.promise.lookups), 
     n.alien.promises=sum(n.alien.promises),
     n.alien.promise.forces=sum(n.alien.promise.forces)
   )

>>>>

``` {r, "basic info", include=FALSE}
# FIXME aggregated_functions <- load_local_csv("aggregated_functions.csv") #

@@

basic_info <- 
  load_local_csv("basic_info.csv") %>%
  group_by(name) %>%
  summarise(
    datasets=paste(name, collapse=", "),
    n.datasets=n(),
    n.functions=sum(as.character(n.functions)),
    n.calls=sum(as.character(n.calls)),
    n.promises=sum(as.character(n.promises)),
    n.promise.forces=sum(as.character(n.promise.forces)),
    n.promise.lookups=sum(as.character(n.promise.lookups)), 
    n.alien.promises=sum(as.character(n.alien.promises)),
    n.alien.promise.forces=sum(as.character(n.alien.promise.forces))
  )

@@

 aggregate_basic_info <- 
   basic_info %>% summarise(
     name="*",
     datasets=paste(name, collapse=", "),
     n.datasets=n(),
     n.functions=NA, # FIXME (aggregated_functions %>% count %>% pull(n)),
     n.calls=sum(n.calls),
     n.promises=sum(n.promises),
     n.promise.forces=sum(n.promise.forces),
     n.promise.lookups=sum(n.promise.lookups), 
     n.alien.promises=sum(n.alien.promises),
     n.alien.promise.forces=sum(n.alien.promise.forces)
   )
